\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliographie}

\bibitem{iso10816} ISO~10816 / ISO~20816, \emph{Mechanical vibration --- Evaluation of
machine vibration by measurements on non-rotating parts}, International Organization for
Standardization.

\bibitem{iso13374} ISO~13374, \emph{Condition monitoring and diagnostics of machines ---
Data processing, communication and presentation} (architecture OSA-CBM), ISO.

\bibitem{iso13373} ISO~13373, \emph{Condition monitoring and diagnostics of machines ---
Vibration condition monitoring}, ISO.

\bibitem{iso13381} ISO~13381, \emph{Condition monitoring and diagnostics of machines ---
Prognostics}, ISO.

\bibitem{iso18436} ISO~18436, \emph{Condition monitoring and diagnostics of machines ---
Requirements for qualification and assessment of personnel}, ISO.

\bibitem{cwru} Case Western Reserve University Bearing Data Center, \emph{Bearing Fault
Dataset}. \url{https://engineering.case.edu/bearingdatacenter}

\bibitem{cmapss} A. Saxena, K. Goebel, D. Simon, N. Eklund, \emph{Damage Propagation
Modeling for Aircraft Engine Run-to-Failure Simulation} (C-MAPSS), International Conference
on Prognostics and Health Management (PHM), 2008.

\bibitem{vbl} VBL-VA001 Vibration Dataset, jeu de données de défauts de machines tournantes.

\bibitem{mcc5} MCC5-THU Gearbox Dataset, Tsinghua University, jeu de données de défauts
d'engrenage.

\bibitem{randall} R. B. Randall, \emph{Vibration-based Condition Monitoring: Industrial,
Aerospace and Automotive Applications}, Wiley, 2011.

\bibitem{xgboost} T. Chen, C. Guestrin, \emph{XGBoost: A Scalable Tree Boosting System},
Proceedings of KDD, 2016.

\bibitem{sklearn} F. Pedregosa et al., \emph{Scikit-learn: Machine Learning in Python},
Journal of Machine Learning Research, vol.~12, 2011.

\bibitem{pytorch} A. Paszke et al., \emph{PyTorch: An Imperative Style, High-Performance Deep
Learning Library}, NeurIPS, 2019.

\bibitem{shap} S. Lundberg, S.-I. Lee, \emph{A Unified Approach to Interpreting Model
Predictions} (SHAP), NeurIPS, 2017.

\bibitem{fastapi} S. Ramírez, \emph{FastAPI --- Modern, fast web framework for building APIs
with Python}. \url{https://fastapi.tiangolo.com}

\bibitem{opcua} OPC Foundation, \emph{OPC Unified Architecture Specification}; bibliothèque
\texttt{asyncua} (FreeOpcUa).

\bibitem{mqtt} OASIS, \emph{MQTT Version 5.0}, OASIS Standard, 2019.

\bibitem{timescale} Timescale Inc., \emph{TimescaleDB --- Time-series database built on
PostgreSQL}. \url{https://www.timescale.com}

\end{thebibliography}
